---
output: github_document
---
<style>
    img {
        border-style: none;
        width: 80%;
        background-color: none;
    }
</style>
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "80%"
)

asciicast::init_knitr_engine(
  startup = quote({
    library(cubepalette)
    set.seed(1) }),
  echo = TRUE,
  echo_input = FALSE
)
```
# cubepalettes

<!-- badges: start -->
<!-- badges: end -->

Colour and palettes as defined in the Cube Group Brand guidelines.

The main purpose of cubepalette is to enable Cube Group staff to use the colours and palettes defined in the brand guidelines within R.

cubepalette was created with the **palettes** package, which provides a comprehensive library for colour vectors and colour palettes using a new family of colour classes (`palettes_colour`, and `palettes_palette`) that always print as hex codes with colour previews. Colour palette packages created with palettes have access to the following capabilities, all without requiring you to write any code: formatting, casting and coercion, extraction and updating of components, plotting, colour mixing arithmetic, and colour interpolation. 

See the following vignettes to learn how to use cubepaellets with other packages:

- [Using palettes with ggplot2](https://mccarthy-m-g.github.io/palettes/articles/ggplot2.html)
- [Using palettes with gt](https://mccarthy-m-g.github.io/palettes/articles/gt.html)
- [Using palettes with biscale](https://mccarthy-m-g.github.io/palettes/articles/biscale.html)
- [Compatibility with other colour packages](https://mccarthy-m-g.github.io/palettes/articles/compatibility.html)

## Included Colours

Cube Group's colour palette uses modern and distinctive tones to convey corporate warmth.

### Cube Green

```{r echo=FALSE, out.height="30px"}
library(cubepalette)
plot(cube.green)
```

`cube.green` is used in majority, bringing maturity and a seriousness when needed.

### Cube Pink

```{r echo=FALSE, out.height="30px"}
plot(cube.pink)
```

`cube.pink` adds warmth, livening up layouts and highlighting key information.

### Cube Grey

```{r echo=FALSE, out.height="30px"}
plot(cube.grey)
```

`cube.grey` is used as a neutral background colour.

### Cube Black and Cube White

`cube.black` and `cube.white` are convenience names for `black` and `white` that allow for consistent syntax when using cubepalette. 


## Installation

You can install the development version of cubepalette from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zerogetsamgow/cubepalette")
```

## Usage

```{r}
library(cubepalette)
```

cubepalette comes with a set of `r length(cube_palettes_discrete)` discrete colour palettes, and `r length(cube_palettes_tints)` sequential colour palettes, which can be accessed from the following R objects:

- `cube_palettes_discrete` for discrete palettes
- `cube_palettes_tints` for sequential palettes
- `cube_palettes` for all palettes

### Discrete

Discrete palettes for use with various backgrounds are available. `dark`, `light` and `other` have been compiled to work on backgrounds composed of colours from the Cube Group brand guideline.

```{r plot-cube-palettes-discrete}
plot(cube_palettes_discrete)
```

### Tints

For long form documents infographics and charts, tints from the Cube Group colour palette can be used in 20 per cent increments. `cube_palettes_tints` is populated with compliant `greens`, `pinks` and `greys`.

```{r plot-cube-palettes-tints}
plot(cube_palettes_tints)
```

Palettes can be subset using `[`, `[[`, and `$`.

  - To extract one or more palettes use `[`:

    ```{asciicast extract-palette}
    cube_palettes_tints[c("greens", "greys")]
    ```
  
  - To extract a single palette as a colour vector use `[[` or `$`:

    ```{asciicast extract-vector-1}
    cube_palettes_tints[["pinks"]]
    ```
    
    ```{asciicast extract-vector-2}
    cube_palettes_tints$pinks
    ```
    
  - To get names of palettes use `names()`:

    ```{r}
    names(cube_palettes_tints)
    ```

## Documentation

See also documentation for the palettes package at [`https://mccarthy-m-g.github.io/palettes/`](https://mccarthy-m-g.github.io/palettes/reference/index.html) or in the installed package: `help(package = "palettes")`.

